Regression Cube Analysis of Cohort Study Data

### 2015-03-28 draft.tex
revised captions, filled gaps in Application section

\subsection{Abstracting Regression Results using $R^2$}
\begin{figure}[htb]
 \centering
 \includegraphics[width=3.5in]{figures/cube}
 \caption{
 (a) Overview visualization using a heatmap for the formula $Z \sim X + Y$, where $Z$ assumes feature $Age$.
 %%
 The $R^2$ values extracted from the regression formulas depict the goodness of fit and are mapped to color saturation.
 %%
 A saturated color shows a strong correlation.
 %%
 (b) Since $Z$ assumes all features $n$ as given by the formula, it yields $n$ heatmap visualizations.
 %%
 These represent the slices in our cube visualization.
 %%
 The $R^2$ values of each slice voxel is mapped on opacity in the 3D-view, reducing the occlusion of other values.
 }
  \label{fig:Cube}
\end{figure}
%%
The goal of an overview visualization is to provide a comprehensive view on the data (raw or using descriptive metrics \cite{Bertini}), which is easy to understand.
%% TODO: Cite another paper here!
As described in our previous work \cite{Klemm2014VIS}, correlation values scaled between 0 (no correlation) and 1 (perfect correlation) can be encoded using color on a mosaic plot.
%%
Regression models are more complex, having many associated describing metrics.
%%
For the \emph{Regression Cube} analysis we are interested in the goodness of fit of the resulting model, which allows to infer about the predictive quality of the independent features included in the model.
%%
As described in Section~\ref{sec:RegressionAnalysis}, the $R^2$ value is the metric allowing for this kind of assessment.
%%
\paragraph{2D (Slice) View.}
%%
Since $R^2$ is scaled between [0,1], it allows for comparison between regression models.
%%
We can apply the same mosaic plot mapping by translating the $R^2$ values to color saturation (Fig.~\ref{fig:Cube} a).
%%
This describes a 2D regression square for dynamic variables $X$ and $Y$ (e.g. $Age \sim X + Y$).
%%

@@

\subsection{Analysis Workflow}
%%
\begin{figure}[htb]
 \centering
 \includegraphics[width=3.0in]{figures/workflow}
 \caption{
 Workflow of the analysis using \emph{Regression Cubes}.
 %%
 [\textbf{1.AF}] The analysis starts with a set of features given by the data set.
 %%
 Then, the user may specify a formula regarding to specify a hypothesis, or use a predefined formula to start a explorative analysis of the data set.
 %%
 [\textbf{2.SI}] The Regression Cube is then visualized, where the user has either the option to adjust the formula or to derive details on demand on a specific regression.
 %%
 [\textbf{3.ZF}] Insights into the data yield either an adjustment of the current formula.
 %%
 By applying a difference view, regression cubes can be compared to each other.
 %%
 [\textbf{4.DD}] Details about features using the 2D-heatmap representation yields insights and hypothesis about feature relations.
 }
  \label{fig:Workflow}
\end{figure}
%%
%\com{Different Formulas work as different steps in the analysis (Fig.~\ref{fig:Workflow})}
%\com{Workflow for different analysis approaches.}
%\com{0. Select the Variables.}
%\com{1. Select the Formulas}
%\com{a) Analysis without hypothesis about the data set (z ~ x+y)}
%\com{b) Analysis without hypothesis with confounder (z ~ age)}
%\com{c) Analysis with hypothesis about the data set (Var ~ x+y+z)}
%\com{d) Use Difference View}
%\com{d) Clarify using confounder (Var ~ x)}
%\com{3. Find interesting pane.}
%\com{4. Get Details on Demand.}
%%
The analysis workflow follows the Visual Analytics (VA) Mantra of Keim et al. \cite{Keim}:

@@

 (c) 2D mosaic plot visualization of the selected slice.

@@

 \com{TODO: Adapt formula to final image.}

@@

 Context information is shown for the regression model of $Parenchym \sim Bronchitis + AlcoholLast30Days$, depicting details about the confidence intervals, coefficients and associated p-values.

@@

\paragraph{3D-Prism as Data Mini-Map.}
%%
The 3D-cube representation acts as an overview over the whole data set, but its purpose is not to derive detailed information about data points.
%%
It serves an function similar to a mini-map, guiding the attention towards points of interest in the data, as well as giving context information about adjacent data values when using the 2D mosaic plot.
%%
It serves the purpose of \emph{Show the Results} after the \emph{Analyze First} step in Keim's VA-Mantra.
%%
The displayed prism shows values above the matrix diagonal.
%%
%% TODO: Add reference for disadvantages of 3D information visualizations!
\paragraph{Tackling the disadvantages of 3D information visualization.}
3D-Information visualizations are often criticized for introducing occlusions and interaction problems, which often do not balance out the advantages of using the third dimension for visual mapping.
%%
We aim to minimize these problems as much as possible.
%%
Since the $R^2$ values are mapped on data point opacity, only large values are highlighted in the prism, guiding the focus to the respective slices.
%%
It also creates a very sparse representation, since the majority of regression models yield (depending on the data set and the chosen formula) low $R^2$ values.
%%
Also, the preceding correlation based feature selection reduces the information space significantly, leading to sparse cubes.
%%
Overlapping is still an issue, but this way greatly reduced in its affect to the readability of the visualization.
%%

@@

\section{Implementation} \label{implementation}
\begin{figure}[htb]
 \centering
 \includegraphics[width=3.5in]{figures/implementation}
 \caption{
 \com{Describe the Bootstrap/Angular/D3 Frontend, Node backend, R/OCPU Backend.}
 }
  \label{fig:Implementation}
\end{figure}
%%
% Using web technologies for prototyping allows for:
% \begin{itemize}
% 	\item easy exchange of software, without the need of installing anything other than a modern web browser,
% 	\item fast iterative adaption of method changes, without the need of installing updates,
% 	\item outsourcing computation-heavy tasks to server-clusters, which do not have to be in local proximity.
% \end{itemize}
% %%
%%
We rely on web-based technologies for our prototype.
%%
The ongoing transition of open-science software into the web spawned numerous projects, making state-of-the-art algorithms available in this domain.
%%
\paragraph{Front-End.}
%%
The front-end is created using \texttt{HTML5}, \texttt{CSS3} and \texttt{Javascript}.
%%
\texttt{Angular.js}\footnote{Open Source; Maintained by Google, \href{https://www.angularjs.org/}{\texttt{angularjs.org}}} abstracts web application into models and views, allowing for a responsive way to combine \texttt{HTML} and \texttt{Javascript}.
%%
\texttt{Angular.js} is forcing developers to write modularized code, which makes the components easier expandable while keeping the code maintainable by including unit tests.
%%
The page layout is handled using \texttt{Twitter Bootstrap}\footnote{Open Source; Maintained by Twitter, \href{http://getbootstrap.com}{\texttt{getbootstrap.com}}}, which also provides a rich set of UI elements with proper stylings.
%%
The 2D mosaic plot is implemented using \texttt{Data driven Documents} (\texttt{D3.js}), which is popular in information visualization using vector graphics \cite{D3}.
%%
It provides fast and easy methods for binding data to graphical elements.
%%
The 3D plot is created using the WebGL-based \texttt{Threejs}\footnote{Open Source; Originally developed by R. Cabello, \href{http://threejs.org}{\texttt{threejs.org}}} library.
%%
We experimented with different ways for achieving the cube representation, including volume rendering, cube primitives for each data point and shader-based solutions.
%%
Open source volume rendering methods are available but do not satisfy our requirements.
%%
Creating a cube primitive for each data point resulted in non-interactive frame-rates for data sets larger than 30 features (creating 30$^3$ cube primitives).
%%
We use a shader-based solution by rendering the cube as a sprite based particle system, allowing to customize color and opacity of every data point.
%%
It also is the fastest solution that we tested.

@@

\section{Application} \label{application}
%%
\begin{figure*}[htb]
 \centering
 \includegraphics[width=7.0in]{figures/application}
 \caption{
 \com{Screenshots of Cubes from the Evaluation}
 }
  \label{fig:Application}
\end{figure*}
%%
In this section, we describe how we applied the \emph{Regression Cube} to two epidemiological data sets.
%%
The hepatic steatosis data set was analyzed using data mining algorithms, yielding risk groups, which we now analyze further.
%%
Also, we try to reproduce the prior results from this analysis as proof-of-concept of our method.
%%
The breast fat data set is the foundation for an explorative analysis towards the influencing parameters of the parenchyma tissue of the female breast.
%%

@@

\subsection{Case 2: Hypothesis-driven Analysis of the Hepatic Steatosis Data Set}
%%
We refer to each analysis step regarding to their belonging in the VA-Mantra (Subsec.~\ref{sec:Workflow}).
%%
The analysis goal is reproducing results based \cite{Niemann2014}.
%%
Therefore, \emph{UN} started the \textbf{AF} step using the dichotomized MRI fat liver concentration using the formula $mrt\_liverfat\_s2 \sim X + Y + Z$ for \emph{male} subjects.
%%
The \emph{SI} step using the 3D cube representations hotspots at the end of the cube (Fig.~\ref{fig:application} a).
%%
\textbf{ZF} by slicing through the cube using the mouse input to inspect the hotspots using the mosaic plot (\textbf{DD}) revealed high correlations for somatometric features, hepatic steatosis indicator-features as well as laboratory values, such as creatinine (\com{important for kidney}) and uric acid (\com{gout, diabetes}) magnitudes.
%%
Similar results present for analyzing the \emph{female} groups.
%%
\emph{UN} could reproduce most results, some features features exhibit lower correlations though, e.g., creatinine magnitudes.
%%
Relationships not described in \cite{Niemann2014} were found, such as enzymes indicating liver dysfunctions, e.g. \emph{aspartate aminotransferase}.
%%
Due to the difference between our regression-model approach and the decision-tree approach presented in \cite{Niemann2014}, a complete matching set of correlating features are not expected.

@@

\textbf{Interleukin-6 correlation with liver fat.}
%%
During the analysis, one hotspot was always observed in the \emph{SI} and \emph{ZF} incorporating a high \emph{Interleukin-6} (\emph{IL-6}) correlation with liver fat values (Fig.~\ref{fig:Application} b).
%%
The correlation was high for both the dichotomized and continuous target feature.
%%
In the literature, relations between liver cancer \cite{He2013} and also chronic liver diseases \cite{Streetz2003}.
%%
Strong effects of \emph{IL-6} with hepatic steatosis were also prior described with mice \cite{Hong2004}.
%%
The finding is subject of further analysis.
%%
\subsection{Further Feedback and Lessons Learned} \label{Lessons Learned}
%%
\textbf{Extracted Hypotheses have to investigated further.}
\com{Tills Feedback - Regression analysis also incorporates assumptions about the data, }
%%

@@

%%
\textbf{Using non-discretized features reduces information bias.}
%%
\com{Comment on the lesson learned from the last VAST Paper - "Usage of different categorizations depending on expected outcome." Now we have continuos data.}
%%

\textbf{Attention steering is crucial.}
\com{Bring important events to the users attention, otherwise it might be overlooked!}

\textbf{Support for different subject groups.}
\com{Include this?}
%%
\com{Feedback from the evaluation goes here.}
\com{Time-aspect critical, interactive analysis requires for fast response. The method needs to be speeded up.}

>>>>

\subsection{Abstracting Regression Results using $R^2$}
\begin{figure}[htb]
 \centering
 \includegraphics[width=3.5in]{figures/cube}
 \caption{
 (left) Overview visualization using a mosaic plot for the formula $Z \sim X + Y$, where $Z$ assumes feature $Age$.
 %%
 The $R^2$ values extracted from the regression formulas depict the goodness of fit and are mapped to color saturation.
 %%
 A saturated color shows a strong correlation.
 %%
 (right) Since $Z$ assumes all features $n$ as given by the formula, it yields $n$ mosaic plot visualizations.
 %%
 These represent the slices in our cube.
 %%
 The $R^2$ values of each slice voxel is mapped on opacity in the 3D-view later on, reducing the occlusion of other values.
 }
  \label{fig:Cube}
\end{figure}
%%
The goal of an overview visualization is to provide a comprehensive view on the data (raw or using descriptive metrics \cite{Bertini}), which is easy to understand.
%% TODO: Cite another paper here!
As described in our previous work \cite{Klemm2014VIS}, correlation values scaled between 0 (no correlation) and 1 (perfect correlation) can be encoded using color on a mosaic plot.
%%
Regression models are more complex, having many associated describing metrics.
%%
For the \emph{Regression Cube} analysis we are interested in the goodness of fit of the resulting model, which allows to infer about the predictive quality of the independent features included in the model.
%%
As described in Section~\ref{sec:RegressionAnalysis}, the $R^2$ value is the metric allowing for this kind of assessment.
%%
\paragraph{2D (Slice) View.}
%%
Since $R^2$ is scaled between [0,1], it allows for comparison between regression models.
%%
We can apply the same mosaic plot mapping by translating the $R^2$ values to color saturation (Fig.~\ref{fig:Cube} a).
%%
This describes a 2D regression square for dynamic variables $X$ and $Y$ (e.g. $Age \sim X + Y$).
%%

@@

\subsection{Analysis Workflow} \label{sec:Workflow}
%%
\begin{figure}[htb]
 \centering
 \includegraphics[width=3.0in]{figures/workflow}
 \caption{
 Workflow of the analysis using \emph{Regression Cubes}.
 %%
 % The analysis starts with a set of features given by the data set.
 %%
 [\textbf{1.AF}] The workflow starts by declaring formula regarding to specify a hypothesis, or use a predefined formula for a hypothesis-free analysis.
 %%
 [\textbf{2.SI}] The \emph{Regression Cube} is then visualized.
 %%
 The user has the option to either adjust the formula or to derive details on demand on a specific regression.
 %%
 [\textbf{3.ZF}] Insights into the data yield either an adjustment of the current formula or selecting a difference view.
 %%
 The latter is used to compare regression cubes.
 %%
 [\textbf{4.DD}] Details about features using the 2D mosaic plot representation yields insights and hypothesis about feature relations.
 }
  \label{fig:Workflow}
\end{figure}
%%
%\com{Different Formulas work as different steps in the analysis (Fig.~\ref{fig:Workflow})}
%\com{Workflow for different analysis approaches.}
%\com{0. Select the Variables.}
%\com{1. Select the Formulas}
%\com{a) Analysis without hypothesis about the data set (z ~ x+y)}
%\com{b) Analysis without hypothesis with confounder (z ~ age)}
%\com{c) Analysis with hypothesis about the data set (Var ~ x+y+z)}
%\com{d) Use Difference View}
%\com{d) Clarify using confounder (Var ~ x)}
%\com{3. Find interesting pane.}
%\com{4. Get Details on Demand.}
%%
The analysis workflow follows the Visual Analytics (VA) Mantra of Keim et al. \cite{Keim}:

@@

 (c) 2D mosaic plot visualization of the selected slice for feature \emph{Pain/Discomfort}.

@@

 %\com{TODO: Adapt formula to final image.}

@@

 %Context information is shown for the regression model of $Parenchym \sim Bronchitis + AlcoholLast30Days$, depicting details about the confidence intervals, coefficients and associated p-values.

@@

\paragraph{3D-Prism as Data Mini-Map.}
\com{Add section about difference view for static target features.}
%%
The 3D-cube representation acts as an overview over the whole data set, but its purpose is not to derive detailed information about data points.
%%
It serves an function similar to a mini-map, guiding the attention towards points of interest in the data, as well as giving context information about adjacent data values when using the 2D mosaic plot.
%%
It serves the purpose of \emph{Show the Results} after the \emph{Analyze First} step in Keim's VA-Mantra.
%%
The displayed prism shows values above the matrix diagonal.
%%
%% TODO: Add reference for disadvantages of 3D information visualizations!
\paragraph{Tackling the disadvantages of 3D information visualization.}
3D-Information visualizations are often criticized for introducing occlusions and interaction problems, which often do not balance out the advantages of using the third dimension for visual mapping.
%%
We aim to minimize these problems as much as possible.
%%
Since the $R^2$ values are mapped on data point opacity, only large values are highlighted in the prism, guiding the focus to the respective slices.
%%
It also creates a very sparse representation, since the majority of regression models yield (depending on the data set and the chosen formula) low $R^2$ values.
%%
Also, the preceding correlation based feature selection reduces the information space significantly, leading to sparse cubes.
%%
Overlapping is still an issue, but this way greatly reduced in its affect to the readability of the visualization.
%%

@@

\section{Implementation} \label{implementation}
\begin{figure}[htb]
 \centering
 \includegraphics[width=3.5in]{figures/implementation}
 \caption{
 The front-end (left) is written in \emph{HTML5}/\emph{CSS3}/\emph{Javascript} and uses different Javascript libraries, such as \emph{Angularjs}, \emph{Three.js} and D3js.
 %%
 The web-server back-end (right) is written in \emph{Nodejs}, hosting is carried out using \emph{Heroku}.
 %%
 \emph{R} and \emph{OpenCPU} constitute the statistical back-end (top) to compute the \emph{Regression Cubes}.
 %%
 Additional statistical back-ends can be attached to the system to decrease the computation time.
% The number of attached machines to the system 
%    the  the  Describe the Bootstrap/Angular/D3 Frontend, Node backend, R/OCPU Backend.}
 }
  \label{fig:Implementation}
\end{figure}
%%
% Using web technologies for prototyping allows for:
% \begin{itemize}
% 	\item easy exchange of software, without the need of installing anything other than a modern web browser,
% 	\item fast iterative adaption of method changes, without the need of installing updates,
% 	\item outsourcing computation-heavy tasks to server-clusters, which do not have to be in local proximity.
% \end{itemize}
% %%
%%
We rely on web-based technologies for our prototype.
%%
The ongoing transition of open-science software into the web spawned numerous projects, making state-of-the-art algorithms available in this domain.
%%
\paragraph{Front-End.}
%%
The front-end is created using \texttt{HTML5}, \texttt{CSS3} and \texttt{Javascript}.
%%
\texttt{Angular.js}\footnote{Open Source; Maintained by Google, \href{https://www.angularjs.org/}{\texttt{angularjs.org}}} abstracts web application into models and views, allowing for a responsive way to combine \texttt{HTML} and \texttt{Javascript}.
%%
\texttt{Angular.js} is forcing developers to write modularized code, which makes the components easier expandable while keeping the code maintainable by including unit tests.
%%
The page layout is handled using \texttt{Twitter Bootstrap}\footnote{Open Source; Maintained by Twitter, \href{http://getbootstrap.com}{\texttt{getbootstrap.com}}}, which also provides a rich set of UI elements with proper stylings.
%%
The 2D mosaic plot is implemented using \texttt{Data driven Documents} (\texttt{D3.js}), which is popular in information visualization using vector graphics \cite{D3}.
%%
It provides fast and easy methods for binding data to graphical elements.
%%
The 3D plot is created using the WebGL-based \texttt{Threejs}\footnote{Open Source; Originally developed by R. Cabello, \href{http://threejs.org}{\texttt{threejs.org}}} library.
%%
We experimented with different ways for achieving the cube representation, including volume rendering, cube primitives for each data point and shader-based solutions.
%%
Open source volume rendering methods are available but do not satisfy our requirements.
%%
Creating a cube primitive for each data point resulted in non-interactive frame-rates for data sets larger than 30 features (creating 30$^3$ cube primitives).
%%
We use a shader-based solution by rendering the cube as a sprite based particle system, allowing to customize color and opacity of every data point.
%%
It also is the fastest solution that we tested.

@@

\section{Application} \label{application}
%%
\begin{figure*}[htb]
 \centering
 \includegraphics[width=7.0in]{figures/application}
 \caption{
 The analysis of the numerical and dichotomized target feature depicting liver-fat values yields similar results (left).
 %%
 In (a), hotspots for somatometrical features with high correlations were found.
 %%
 High correlations were also found for features depicting \emph{hepatic steatosis} (b).
 %%
 A high correlations between \emph{Interleukin-6}, \emph{hepatic steatosis}, \emph{GGT} and \emph{Lipase} (highlighted using arrows) was found during the analysis using the 2D mosaic plot.
 %%
 \com{Caption Breast Fat Data}
 }
  \label{fig:Application}
\end{figure*}
%%
In this section, we describe how we applied the \emph{Regression Cube} to two epidemiological data sets.
%%
The hepatic steatosis data set was analyzed using data mining algorithms, yielding risk groups, which we now analyze further.
%%
Also, we try to reproduce the prior results from this analysis as proof-of-concept of our method.
%%
The breast fat data set is the foundation for an explorative analysis towards the influencing parameters of the parenchyma tissue of the female breast.
%%

@@

\subsection{Case 2: Hypothesis-driven Analysis of the Hepatic Steatosis Data Set}
\com{Add R$^2$ values}
%%
We refer to each analysis step regarding to their belonging in the VA-Mantra (Sec.~\ref{sec:Workflow}).
%%
The analysis goal is reproducing results based on \cite{Niemann2014}.
%%
Therefore, \emph{UN} started the \textbf{AF} step using the dichotomized MRI fat liver concentration using the formula $mrt\_liverfat\_s2 \sim X + Y + Z$ for \emph{male} subjects.
%%
The \emph{SI} step using the 3D cube representations locates hotspots at the end of the cube (Fig.~\ref{fig:Application} a).
%%
\textbf{ZF} by slicing through the cube using the mouse input to inspect the hotspots using the mosaic plot (\textbf{DD}) revealed high correlations for somatometric features, hepatic steatosis indicator-features as well as laboratory values, such as creatinine (\com{important for kidney}) and uric acid (\com{gout, diabetes}) magnitudes.
%%
Similar results present for analyzing the \emph{female} groups.
%%
\emph{UN} could reproduce most results, some features features exhibit lower correlations though, e.g., creatinine magnitudes.
%%
Relationships not described in \cite{Niemann2014} were found, such as enzymes indicating liver dysfunctions, e.g. \emph{aspartate aminotransferase}.
%%
Due to the difference between our regression-model approach and the decision-tree approach presented in \cite{Niemann2014}, a complete matching set of correlating features are not expected.

@@

\textbf{Interleukin-6 correlation with liver fat.}
%%
During the analysis, one hotspot was always observed in the \emph{SI} and \emph{ZF} incorporating a high \emph{Interleukin-6} (\emph{IL-6}) correlation with liver fat values (Fig.~\ref{fig:Application} b).
%%
The correlation was high for both the dichotomized and continuous target feature.
%%
In the literature, relations between liver cancer \cite{He2013} and also chronic liver diseases \cite{Streetz2003}.
%%
Strong effects of \emph{IL-6} with hepatic steatosis were also prior described with mice \cite{Hong2004}.
%%
The finding is subject of further analysis.
%%
\subsection{Further Feedback and Lessons Learned} \label{Lessons Learned}
%%
Our method was well received among the domain experts.
%%
The novel way of modeling expert knowledge to derive hypothesis driven overview visualizations allow for detailed analysis of target features, either disease indicators or even image-derived features.
%%
%TI commented on the

\textbf{Extracted Hypotheses have to investigated further.}
%%
Agreeing with TI's feedback, each finding and hypotheses has to be confirmed using dedicated statistical analysis.
%%
This incorporated investigating all potential confounding features as well as looking for outlier subjects.
%%
TI commented on the possibility of adding even more regression types to model different correlation types to customize the cube even more.
%%
%TI hinted the neccissity of different regression types, which also model non-linear relationships, but do not comprise of comparable quality of fit measures, such as the $R^2$.
%%
%\com{Tills Feedback - Regression analysis also incorporates assumptions about the data, }
%%

@@

%%
\textbf{Using non-discretized features reduces information bias.}
%%
Discretization reduces the information space and introduces bias into the data and is therefore avoided in epidemiological research when possible.
%%
In contrast to many data mining algorithms, our method allows to use the concurrent analysis of heterogeneous data types.
%%
Investigations of the the hepatic steatosis data set with both numerical and dichotomized liver fat values showed comparable results differing in detail.%, but differences  %differing in detail.
%%
The overall explanatory power towards the numerical feature was lower.
%Our investigation regarding the hepatic steatosis data set confirms differences in results
%%
%\com{Comment on the lesson learned from the last VAST Paper - "Usage of different categorizations depending on expected outcome." Now we have continuos data.}
%%

\textbf{Attention steering is crucial.}
%%
Important events have to be highlighted in overview visualizations to steer the users attention to interesting parts of the data.
%%
Poor guidance lead to potentially overlooked relationships.
%%
We found supporting mini-map visualizations, such as the 3D cube, most useful for this purpose.
%%
Foe example, formulas with a static target feature (e.g. $Breast\_Cancer ~ X + Y + Z$) are rendered by highlighting differences rather than absolute values in the 3D cube visualizations (see Fig.~\ref{fig:Application} left) by comparing local values with the mean along the z ray.
%%

%This allows for fast parsing through the data

%In order to benefit most from the human pattern recognition, interesting events have to highlighted in order to steer the users attention to important parts of the data.
%Using overview visualizations is associated with important 
%\com{Bring important events to the users attention, otherwise it might be overlooked!}

%\textbf{Support for different subject groups.}
%\com{Include this?}
%%
%\com{Feedback from the evaluation goes here.}
%\com{Time-aspect critical, interactive analysis requires for fast response. The method needs to be speeded up.}
